Multi-modality Imagery Database for Plant Phenotyping

### 2015-07-14 datapaper_hardware.tex
revision -JIN v2

Infrared images were collected once every hour with the same camera and filter used for chlorophyll {\it a} fluorescence.
Pulses of $940~nm$ light were provided by an array of OSRAM LEDs (SFH 4239, Digi-Key), collimated using a Polymer Optics lens (Part no. 170, Polymer Optics Ltd., Berkshire, England).
Since $940~nm$ light does not influence plant development or drive photosynthesis, images were also collected during the night period~\cite{eskins1992light}.
%
Precisely, phytochromes are the closest photoreceptors that absorb in the far red, near infrared region, but the action spectrum is diminished to zero or near zero ($>800~nm$) in the region where we do IR reflectance ($940~nm$)~\cite{butler1964actton}.

@@

The imagery data were collected once every hour.
These include the fluorescent image, the IR reflectance image with the same camera, the color image, the $3$D depth and a confidence image.
The $3$D depth image is built from the depth sensor by transforming the points into the world coordinates and is expressed in the unit of $mm$.
The confidence image is the standard deviation of the depth pixels.
This is useful for identifying pixels at depth discontinuities that are unreliably detected and result in large standard deviations.

>>>>

Infrared images were collected once every hour with the same camera and filter used for chlorophyll {\it a} fluorescence.
Pulses of $940~nm$ light were provided by an array of OSRAM LEDs (SFH 4239, Digi-Key), collimated using a Polymer Optics lens (Part no. 170, Polymer Optics Ltd., Berkshire, England).
Since $940~nm$ light does not influence plant development or drive photosynthesis, images were also collected during the night period~\cite{eskins1992light}.
%
Precisely, phytochromes are the closest photoreceptors that absorb in the far red, near infrared region, but the action spectrum is diminished to zero or near zero ($>800~nm$) in the region where we do IR reflectance ($940~nm$)~\cite{butler1964actton}.
%
Note that the other modalities were captured only at day time, so that they will not interfere plant growth.

@@

\subsubsection{Image collection} 
The imagery data, including the fluorescent image, the IR reflectance image,  the color image, and the $3$D depth image, were collected once every hour. First, the fluorescent image and the IR reflectance image were captured sequentially using the same camera without any delay.
% 
After five minutes, the $3$D depth image and the color image were captured using the Creative Senz3D sensor. The captured depth points were then transformed into the world coordinates and expressed in the unit of $mm$. Since plant leaves do not move quickly, the five minutes gap between the camera operations do not cause severe problems in image calibration.

%A confidence image is the standard deviation of the depth pixels.
%This is useful for identifying pixels at depth discontinuities that are unreliably detected and result in large standard deviations.
